Climate change projected to reduce European life expectancy

### 2018-02-19 MS-cclifeexpec.Rmd
fixed some file locations.

lt_lancet <- read.csv("C:/Users/Matt/Documents/Matt - Work Stuff/r code/lt_afterr_09032017.csv")
lt_lifetables <- read.csv("C:/Users/Matt/Documents/Matt - Work Stuff/r code/lancet_lifetables_09032017.csv")

>>>>

lt_lancet <- read.csv("data/lt_afterr_09032017.csv")
lt_lifetables <- read.csv("data/lancet_lifetables_09032017.csv")
